PANCHANGE_analysis

### 2020-09-03 PANCHANGE_analysis.Rmd

# Regression
Regress covariates out of the change? Which?

>>>>

#ANALYSIS PLAN
1. Calculate mean change per disorder group 
    i. Disorders (9)
      a. Rank the disorders by the size of the change
    ii. Sex 
    iii. Age (13; RAMP; potentially collapse above 65 depending on group sizes) 
    iv. Ethnicity groups (5; White European, Black (British), Asian, Arab, Mixed)

2. Regression models (Regress covariates out of the change? Which?)
    i. Model 0: Disorders  
    ii. Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline

3. Re-calculate change

4. Re-rank the change again

5. PCL:  
    i. Calculate the total GLAD, COPING, RAMP baseline
    ii. For each item:
          a. present percentages of how say that this is due to the pandemic 
          b. Calculate a variable PCL pandemic score 
          c. If one item is highly endorsed due to pandemic -> exclude in sensitivity analysis

# 1. Calculate mean change per group

# 2. Regression
Regress covariates out of the change? Which?
